---
title: "lab1"
author: "Полянская Полина Алексеевна"
format:   
  md:
    output-file: README.md
editor_options: 
  chunk_output_type: inline
---

Прохождение курса по R в RStudio через пакет swirl \n
(R Programming: The basics of programming in R)

## Цель

1. Познакомится с синтаксисом языка программирования R \n

2. Оформить отчет \n

## Исходные данные

1.  Ноутбук с ОС Windows 10
2.  RStudio
3.  Пакет swirl

## Решение задачи

Нужно ввести swirl::swirl()

```{r}
5 + 7
```
```{r}
x <- 5 + 7
x
```

```{r}
y <- x - 3
y
```

```{r}
z <- c(1.1, 9, 3.14)
```

```{r}
?c
```

```{r}
z
```

```{r}
c(z, 555, z)
```

```{r}
z * 2 + 100
```

```{r}
my_sqrt <- sqrt(z - 1)
```

| Before we view the contents of the my_sqrt variable, what do you think it contains?

1: a vector of length 0 (i.e. an empty vector) \n
2: a single number (i.e a vector of length 1) \n
3: a vector of length 3 \n

3

```{r}
my_sqrt
```

```{r}
my_div <- z / my_sqrt
```

| Which statement do you think is true?

1: The first element of my_div is equal to the first element of z divided by the first element of my_sqrt, and so on...
2: my_div is undefined
3: my_div is a single number (i.e a vector of length 1)

Выбор:1

```{r}
my_div
```

```{r}
c(1, 2, 3, 4)
```

```{r}
c(1, 2, 3, 4) + c(0, 10)
```

```{r}
c(1, 2, 3, 4) + c(0, 10, 100)
```

